En garde! Unguarded iteration for reversible computation in the Delay monad\thanks{Niccol\`o Veltri was supported by a research grant (13156) from VILLUM FONDEN.}

### 2019-04-30 mpc19/paper.tex
Superposing

\begin{figure}
\[
\arraycolsep=8pt\def\arraystretch{1.8}
\begin{array}{cc} %{|cc|} \hline 
\multicolumn{2}{c}{\mathsf{naturality_L} : f \bullet \trace\,g \LR \trace\,((f \oplus
  \id) \bullet g)} \\ 
\multicolumn{2}{c}{\mathsf{naturality_R} : \trace\,g \bullet f \LR \trace\,(g \bullet (f 
  \oplus \id))} \\  
\multicolumn{2}{c}{\mathsf{dinaturality} : \trace \,((\id \oplus f) \bullet g) \LR \trace
  \,(g \bullet (\id \oplus f))} \\
\multicolumn{2}{c}{\mathsf{vanishing_\oplus} : \trace \,f \LR \trace \,(\trace
  \,(\alpha_\oplus^{-1} \bullet f \bullet \alpha_\oplus))} \\ 
\mathsf{vanishing_\Z} : f \LR \rho_\oplus^{-1} \bullet \trace \,f
  \bullet \rho_\oplus 
&
\mathsf{yanking} : \trace \sigma_\oplus \LR \id
 \\
\multicolumn{2}{c}{\mathsf{tracePIso} : \trace\,f \bullet \trace\,(\dagger\,f)
  \bullet \trace\,f \LR \trace \,f} \\
%%  \\[.25cm]
%% \multicolumn{2}{c}{\infer{\mathsf{tracePIso}\,p : \trace\,f \bullet \trace\,(\dagger\,f)
%%   \bullet \trace\,f \LR \trace \,f}{p : f \bullet \dagger\,f \bullet
%%   f \LR f}} \\
\mathsf{foldIso} : \fold \bullet \unfold \LR \id 
&
\mathsf{unfoldIso} : \unfold \bullet \fold \LR \id
\\
\multicolumn{2}{c}{\mathsf{uniquePIso} : f \bullet \dagger \,f
  \bullet g \bullet \dagger \, g \LR g \bullet \dagger \,g
  \bullet f \bullet \dagger \, f}
%\\ \hline
\end{array}
\]
\caption{Selection of term equivalences of \Pio}
\label{fig:programequivs}
\end{figure}

@@

@@

A selection of term equivalences of \Pio\ is given in Figure
\ref{fig:programequivs}. We only include the equivalences that either
differ or have not previously considered by Carette and Sabry in their
formalization of the finite fragment of \Pio \cite{CaretteS16}. In
particular, we leave out the long list of Laplaza's coherence axioms
expressing that the types of \Pio\ form a rig category \cite{Laplaza}.
We also omit the equivalences stating that $\lambda_\oplus^{-1}$ is
the total inverse of $\lambda_\oplus$, similarly for the other
structural morphisms.

The list of term equivalences in Figure \ref{fig:programequivs}
contains the trace axioms, displaying that the types of \Pio\ form a
traced monoidal category wrt. the additive monoidal structure
$(\Z,\oplus)$ \cite{Karvonen19}. Next we ask for
$\trace\,(\dagger\,f)$ to be the partial inverse of
$\trace\,f$. Remember that we have defined $\dagger\,(\trace\,f)$ to
be $\trace\,(\dagger \,f)$, so the axiom $\mathsf{tracePIso}$
is evidence that the trace combinator of \Pio\ is a dagger trace.
Afterwards we have two equivalences stating that $\unfold$ is the
total inverse of $\fold$.

>>>>

@@

\begin{figure}
\[
\arraycolsep=8pt\def\arraystretch{1.8}
\begin{array}{cc} %{|cc|} \hline 
\multicolumn{2}{c}{\mathsf{naturality_L} : f \bullet \trace\,g \LR \trace\,((f \oplus
  \id) \bullet g)} \\ 
\multicolumn{2}{c}{\mathsf{naturality_R} : \trace\,g \bullet f \LR \trace\,(g \bullet (f 
  \oplus \id))} \\  
\multicolumn{2}{c}{\mathsf{dinaturality} : \trace \,((\id \oplus f) \bullet g) \LR \trace
  \,(g \bullet (\id \oplus f))} \\
\multicolumn{2}{c}{\mathsf{superposing} : \trace \,(\alpha_\oplus^{-1}
  \bullet (\id \oplus f) \bullet \alpha_\oplus) \LR \id \oplus \trace \,f} \\ 
\multicolumn{2}{c}{\mathsf{vanishing_\oplus} : \trace \,f \LR \trace \,(\trace
  \,(\alpha_\oplus^{-1} \bullet f \bullet \alpha_\oplus))} \\ 
\mathsf{vanishing_\Z} : f \LR \rho_\oplus^{-1} \bullet \trace \,f
  \bullet \rho_\oplus 
&
\mathsf{yanking} : \trace\, \sigma_\oplus \LR \id
 \\
\multicolumn{2}{c}{\mathsf{tracePIso} : \trace\,f \bullet \trace\,(\dagger\,f)
  \bullet \trace\,f \LR \trace \,f} \\
%%  \\[.25cm]
%% \multicolumn{2}{c}{\infer{\mathsf{tracePIso}\,p : \trace\,f \bullet \trace\,(\dagger\,f)
%%   \bullet \trace\,f \LR \trace \,f}{p : f \bullet \dagger\,f \bullet
%%   f \LR f}} \\
\mathsf{foldIso} : \fold \bullet \unfold \LR \id 
&
\mathsf{unfoldIso} : \unfold \bullet \fold \LR \id
\\
\multicolumn{2}{c}{\mathsf{uniquePIso} : f \bullet \dagger \,f
  \bullet g \bullet \dagger \, g \LR g \bullet \dagger \,g
  \bullet f \bullet \dagger \, f}
%\\ \hline
\end{array}
\]
\caption{Selection of term equivalences of \Pio}
\label{fig:programequivs}
\end{figure}

@@

A selection of term equivalences of \Pio\ is given in Figure
\ref{fig:programequivs}. We only include the equivalences that either
differ or have not previously considered by Carette and Sabry in their
formalization of the finite fragment of \Pio~\cite{CaretteS16}. In
particular, we leave out the long list of Laplaza's coherence axioms
expressing that the types of \Pio\ form a rig category \cite{Laplaza}.
We also omit the equivalences stating that $\lambda_\oplus^{-1}$ is
the total inverse of $\lambda_\oplus$, similarly for the other
structural morphisms.

The list of term equivalences in Figure \ref{fig:programequivs}
contains the trace axioms, displaying that the types of \Pio\ form a
traced monoidal category wrt. the additive monoidal structure
$(\Z,\oplus)$ \cite{JoyalSV96}. Next we ask for
$\trace\,(\dagger\,f)$ to be the partial inverse of
$\trace\,f$. Remember that we have defined $\dagger\,(\trace\,f)$ to
be $\trace\,(\dagger \,f)$, so the axiom $\mathsf{tracePIso}$
is evidence that the trace combinator of \Pio\ is a dagger trace.
Afterwards we have two equivalences stating that $\unfold$ is the
total inverse of $\fold$.
